---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sirstochastic

<!-- badges: start -->
<!-- badges: end -->

The goal of package sirstochastic is to run simulations of single and multiple iterations of the SIR stochastic model.

## Installation

You can install the released version of sirstochastic from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sirstochastic")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("reside-ic/sirstochastic")
```

## Equations
The equations defining the model are:

* dS/dt = - beta * S * I / N
* dI/dt = beta * S * I / N - sigma * I
* dR/dt = sigma * I


and these are converted to the discrete stochastic model by imagining that in a small period of time `dt` the chance of an event happening follows a Bernoulli trial. In a discrete time step of size `dt` we model the number of infections (i.e., the number of individuals who move from `S` to `I`) as a binomial draw with `n = S` and `p = beta * I / N * dt`) and the number of recoveries (movements from `I` to `R`) as a binomial draw with `n = I` and `p = sigma * dt`. Note, N = S + I + R.

## Example

This is a basic example which shows you how to solve a common problem. The model is run once for 10,000 iterations with a time step of 0.01

```{r echo=FALSE, fig.cap = "SIR simulation run once, N= 10000, dt = 0.01"}
dt <- 0.01
results <- sirstochastic::themodel(dt)

sir_col <- c("#8c8cd9", "#cc0044", "#999966")
par(mar = c(4.1, 5.1, 0.5, 0.5), las = 1)
matplot(results$time[1:10000], cbind(results$S[1:10000], results$I[1:10000], results$R[1:10000]), type = "l", col = sir_col, lty = 1, xlab="time", ylab="S, I, R")
legend("topright", inset = 0.05, lwd = 1, col = sir_col, legend = c("S", "I", "R"))
```

This time the model is run ten times for 10,000 iterations with a time step of 0.01 using the same code.

```{r echo=FALSE, fig.cap = "SIR simulation run 10 times, N= 10000, dt = 0.01"}
dt <- 0.01
count <- 1:10

for (j in count)
  {
    results <- sirstochastic::themodel(dt)
    
    sir_col <- c("#8c8cd9", "#cc0044", "#999966")
    par(mar = c(4.1, 5.1, 0.5, 0.5), las = 1, new=TRUE)
    matplot(results$time[1:10000], cbind(results$S[1:10000], results$I[1:10000], results$R[1:10000]), type = "l", col = sir_col, lty = 1, xlab="time", ylab="S, I, R")
    legend("topright", inset = 0.05, lwd = 1, col = sir_col, legend = c("S", "I", "R"))
}
```

## License

MIT © Imperial College of Science, Technology and Medicine

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
