---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sirstochastic

<!-- badges: start -->
[![R build status](https://github.com/reside-ic/sirstochastic/workflows/R-CMD-check/badge.svg)](https://github.com/reside-ic/sirstochastic/actions)
<!-- badges: end -->

The goal of package sirstochastic is to run simulations of single and multiple iterations of the SIR stochastic model, compartmental and individual.

## Installation

You can install the released version of sirstochastic from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sirstochastic")
install.packages("ggplot2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("reside-ic/sirstochastic")
```
##COMPARTMENTAL
## Equations
The equations defining the model are:

* dS/dt = - beta * S * I / N
* dI/dt = beta * S * I / N - sigma * I
* dR/dt = sigma * I


and these are converted to the discrete stochastic model by imagining that in a small period of time `dt` the chance of an event happening follows a Bernoulli trial. In a discrete time step of size `dt` we model the number of infections (i.e., the number of individuals who move from `S` to `I`) as a binomial draw with `n = S` and `p = beta * I / N * dt`) and the number of recoveries (movements from `I` to `R`) as a binomial draw with `n = I` and `p = sigma * dt`. Note, N = S + I + R.

## Example

This is a basic example which shows you how to solve a common problem. The model is run once for 10,000 iterations with a time step of 0.01.

```{r 1run10000points, echo=FALSE}
options(warn = - 1) 
pars <- sirstochastic::get_parameters()
end_time <- 100

df <- sirstochastic::compartmental_sirmodel(end_time, pars)
sirstochastic:::displaythemodel(df)

```

This time the model is run a 100 times for 10,000 iterations with a time step of 0.01 using the same code.

```{r 100runs10000points, echo=FALSE}
options(warn = - 1) 
pars <- sirstochastic::get_parameters()
end_time <- 100

df <- lapply(seq_len(100), function(simulation) sirstochastic::compartmental_sirmodel(end_time, pars))

sirstochastic:::displaythemodel(df) 

```
## INDIVIDUAL

```{r individual_toy}
library('remotes')
install_github('mrc-ide/individual')
library(individual)
library(ggplot2)
library(reshape2)

# population <- 10000
# average_age <- 30
# S <- State$new('S', population)
# I <- State$new('I', 0)
# R <- State$new('R', 0)
# birth <- Variable$new('birth', rexp(population, 1/average_age))
# human <- Individual$new('human', list(S, I, R))
# 
# render_state_sizes <- function(api) {
#   api$render('susceptable_counts', length(api$get_state(human, S)))
#   api$render('infected_counts', length(api$get_state(human, I)))
#   api$render('recovered_counts', length(api$get_state(human, R)))
# }

# R_t <- 0.2

# # we want to move individuals from S to I with rate R based on infected people in the population
# infection_process <- function(api) {
#   n_to_infect <- length(api$get_state(human, I)) * R_t
#   infected <- sample.int(length(api$get_state(human, S)), n_to_infect)
#   api$queue_state_update(human, I, infected)
# }
# 
# S <- State$new('S', population)
# I <- State$new('I', 10)
# R <- State$new('R', 0)
# human <- Individual$new('human', list(S, I, R))

# output <- simulate(human, list(infection_process, render_state_sizes), 10000)
# 
# # plot_states <- function(df) {
# #   ggplot(
# #     melt(df, 'timestep'),
# #     aes(x = timestep, y = value, group = variable)
# #   ) + geom_line(aes(color = variable))
# # }
# sirstochastic:::plot_states(output)
```

# SIR individul model with compartmental probabilities
```{r 1run10000pointsindividual, echo=FALSE}
library('remotes')
install_github('mrc-ide/individual')
library(individual)
library(ggplot2)
library(reshape2)

options(warn = - 1) 
pars <- sirstochastic::get_parameters()
end_time <- 100

output <- sirstochastic::individual_sirmodel(end_time, pars)

sirstochastic:::plot_states(output)

```
## License

MIT © Imperial College of Science, Technology and Medicine

