---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sirstochastic

<!-- badges: start -->
<!-- badges: end -->

The goal of package sirstochastic is to run simulations of single and multiple iterations of the SIR stochastic model.

## Installation

You can install the released version of sirstochastic from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sirstochastic")
install.packages("ggplot2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("reside-ic/sirstochastic")
```

## Equations
The equations defining the model are:

* dS/dt = - beta * S * I / N
* dI/dt = beta * S * I / N - sigma * I
* dR/dt = sigma * I


and these are converted to the discrete stochastic model by imagining that in a small period of time `dt` the chance of an event happening follows a Bernoulli trial. In a discrete time step of size `dt` we model the number of infections (i.e., the number of individuals who move from `S` to `I`) as a binomial draw with `n = S` and `p = beta * I / N * dt`) and the number of recoveries (movements from `I` to `R`) as a binomial draw with `n = I` and `p = sigma * dt`. Note, N = S + I + R.

## Example

This is a basic example which shows you how to solve a common problem. The model is run once for 10,000 iterations with a time step of 0.01.

```{r echo=FALSE}

options(warn = - 1) 

pars <- sirstochastic::get_parameters()
end_time <- 100

df <- sirstochastic::sirmodel(end_time, pars)
sirstochastic:::displaythemodel(df)

```

This time the model is run a 100 times for 10,000 iterations with a time step of 0.01 using the same code.

```{r echo=FALSE}
options(warn = - 1) 

pars <- sirstochastic::get_parameters()
end_time <- 100

df <- lapply(seq_len(100), function(simulation) sirstochastic::sirmodel(end_time, pars))

sirstochastic:::displaythemodel(df) 

```

## License

MIT © Imperial College of Science, Technology and Medicine

